Co-methylation

### 2015-05-06 Rmarkdown/comethylation.Rmd
Reword convergence discussion

To begin, we explore the effect of the marginal probabilities, $\pi_{2 +}, \pi_{+ 2}$, when $\theta = 0$ ($\psi = 1$) identically across the $K$ tables (corresponding to independence of $X$ and $Y$) for $K = 100$ (Simulation 1a, Figure \ref{fig:Simulation_1a}), and $K = 1000$ (Simulation 1b, Figure \ref{fig:Simulation_1b}). Under this simulation, we expect both $\widehat{\theta}_{U}$ and $\widehat{\theta}_{MH}$ to converge to the true value, $\theta = 0$, as $K \to \infty$. This is indeed what we observe, except when the marginal probabilities are uniformly near the boundaries ($\pi_{2 +} = \pi_{+ 2} = 0.01$ and $\pi_{2 +} = \pi_{+ 2} = 0.99$) and $K$ is small. By contrast, the estimates of $\theta$ from the individual $2 \times 2$ tables, $\widehat{\theta}_{0.5}$, are highly biased, even when $K = 1000$ in Simulate 1b (Figure \ref{fig:Simulation_1b}). In both Simulation 1a and 1b (Figures \ref{fig:Simulation_1a} and \ref{fig:Simulation_1b}) the histograms of $\widehat{\theta}_{0.5}$ are not centred around the true value, $\theta = 0$, unless the marginal probabilities are well away from the boundaries ($0.25 < \pi_{2 +} = \pi_{+ 2} < 0.75$).

>>>>

To begin, we explore the effect of the marginal probabilities, $\pi_{2 +}$ and $\pi_{+ 2}$, when $\theta = 0$ ($\psi = 1$) identically across the $K$ tables (corresponding to independence of $X$ and $Y$) for $K = 100$ (Simulation 1a, Figure \ref{fig:Simulation_1a}), and $K = 1000$ (Simulation 1b, Figure \ref{fig:Simulation_1b}). In this setting we expect both $\widehat{\theta}_{U}$ and $\widehat{\theta}_{MH}$ to converge to the true value, $\theta = 0$, as $K \to \infty$. The rate of convergence, however, also depends on the the marginal probabilities, $\pi_{2+}$ and $\pi_{+2}$. We see that when the marginal probabilities are uniformly near the boundaries ($\pi_{2 +} = \pi_{+ 2} = 0.01$ and $\pi_{2 +} = \pi_{+ 2} = 0.99$), that the approximation is poor when $K = 100$ (Simulation 1a, Figure \ref{fig:Simulation_1a}) but is reasonable when $K = 1000$ (Simulation 1b, Figure \ref{fig:Simulation_1b}). Regardless of whether $K = 100$ or $K = 1000$, the histograms of $\widehat{\theta}_{0.5}$ are not centred around the true value, $\theta = 0$, unless the marginal probabilities are well away from the boundaries ($0.25 < \pi_{2 +} = \pi_{+ 2} < 0.75$).
